%-------------------------
% Resume in Latex
% Author : Nathan Card
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.75in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    \textbf{\Huge Nathan Card} \\ \vspace{1pt}
    \small 613-921-6990 $|$ \href{mailto:x@x.com}{\underline{ncard24@gmail.com}} $|$ 
    \href{https://linkedin.com/in/nathan-card-dev}{\underline{linkedin.com/in/nathan-card-dev}} $|$
    \href{https://github.com/natecard}{\underline{github.com/natecard}}
\end{center}

\section{Summary}
\begin{itemize}[leftmargin=0.15in, rightmargin=0.15in, label={}]
  \small{\item

  {Seasoned entrepreneur and business leader transitioning to software engineering after 8+ years of successful ownership and operations management.}
  {Nearing completion of a Master's in Computer Science with a strong foundation in AI, machine learning, and data analytics.}
  {Adept at understanding business requirements and technical specifications to develop innovative solutions.}
  {Innate problem-solver and quick learner, thriving in dynamic team environments.}

    % {Passionate about leveraging cutting-edge technologies to develop innovative solutions that drive business growth and enhance user experiences.}
    % {Skilled in Python, Rust, JavaScript, and various frameworks and libraries to design, develop, and deploy software applications.}
    }
  \end{itemize}      
    
%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University of York}{York, UK}
      {Master of Science in Computer Science: Artificial Intelligence}{May 2023 -- May 2025}
\resumeItemListStart
      \resumeItem{Relevant Coursework: Artificial Intelligence and Machine Learning, Advanced Data Structures and Algorithms, Applied Artificial Intelligence, Big Data Analytics, Advanced Programming Techniques, Software Engineering.}
      \resumeItemListEnd
  %   \resumeSubheading
  %     {Trent University}{Peterborough, ON}
  %     {Bachelor of Arts Honours in History}{Sept. 2010 -- May 2015}
  \resumeSubHeadingListEnd
%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{Generative AI Prompter} $|$ \emph{Python, Langchain, Streamlit, Ollama}}{Mar. 2024 -- Present}
          \resumeItemListStart
            \resumeItem{Developed a Python-based program to refine and optimize prompts using open source large language models (LLM) to perform natural language processing (NLP).
            \small{
            \textcolor{white}{
              version control, software development life cycle, nosql, HTML}
              }}
            \resumeItem{Integrated Langchain's language model capabilities to fine-tune the prompt generation process.}
            \resumeItem{Designed a user-friendly interface for seamless prompt input, output, and iterative refinement.}
            \resumeItem{Documented the architecture, functionality, and usage guidelines for maintenance and future enhancements.}
          \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{Pomodoro Timer} $|$ \emph{Rust, Next.JS, Tauri}}{Nov. 2023 -- Jan. 2024}
          \resumeItemListStart
            \resumeItem{Developed a cross-platform Pomodoro timer application using Tauri for full functionality on macOS and Windows.}
            \resumeItem{Utilized Rust for the backend, capitalizing on its performance and reliability, and integrated it with Next.js.}
            \resumeItem{Implemented the Pomodoro method, including work intervals and breaks, to help users boost productivity levels.}
            \resumeItem{Crafted a user-friendly interface with intuitive controls, visual timers, and customization options to cater to individual user preferences.
            \small{
            \textcolor{white}{
              code review, frontend, backend, front-end, fullstack, Agile, REST APIs, CSS}
            }}
         
          \resumeItemListEnd
          \resumeProjectHeading
          {\textbf{British Radio Tower Tracker} $|$ \emph{Python, Seaborne, NumPy, Pandas, Matplotlib}}{Sept. 2023 -- Dec. 2023}
          \resumeItemListStart
          \resumeItem{Built a robust data extraction and processing pipeline to track 180+ British radio towers, leveraging Python's capabilities for large datasets.
          \small{
            \textcolor{white}{
          tensorflow, keras, rdbms, database management, test-driven development
          }
          }}
          \resumeItem{Implemented data validation and error-handling to ensure integrity and reliability of the radio tower information.}
          \resumeItem{Designed data visualizations using Seaborn and Matplotlib, enabling users to easily interpret and analyze the radio tower data with a proven accuracy of 95+\%.}
          \resumeItemListEnd
          \resumeSubHeadingListEnd
          

% Agile REST APIs Web Development Software Testing database design API testing SDLC full stack tdd Wepack

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Student Tutor}{October 2023 -- Present}
      {University of York}{York, UK}
      \resumeItemListStart
      \resumeItem{Facilitate weekly tutoring sessions for CS students, leading to a 25\% improvement in their project grades.}
      \resumeItem{Review code, debug issues, and provide constructive feedback to help students improve their programming skills and project deliverables.
      \small{
    \textcolor{white}{back-end, full-stack, Web Development, node js, react js, pytorch
      }\\
      }}
      \resumeItem{Demonstrate strong communication and interpersonal skills in facilitating discussions and fostering collaborative learning environments.
          \small{
        \textcolor{white}{Software Testing, database design, API testing, SDLC, full stack, tdd, Webpack
          }\\
          }}
    \resumeItemListEnd
      
% -----------Multiple Positions Heading-----------
%    \resumeSubSubheading
%     {Software Engineer I}{Oct 2014 - Sep 2016}
%     \resumeItemListStart
%        \resumeItem{Apache Beam}
%          {Apache Beam is a unified model for defining both batch and streaming data-parallel processing pipelines}
%     \resumeItemListEnd
%    \resumeSubHeadingListEnd
%-------------------------------------------

    \resumeSubheading
      {Head of Operations/Co-Founder}{May 2015 -- Sept. 2023}
      {Wild Card Brew Co.}{Trenton, Ontario, Canada}
      \resumeItemListStart
      \resumeItem{Developed, managed, and updated an e-commerce store that generated \$1.5M+ in revenue over 6 years.}
      \resumeItem{Managed a team of 6 employees to launch a hard goods company that achieved Nationwide distribution.}
      \resumeItem{Fostered a collaborative and mentorship-focused approach to build organizational capacity.}
      \resumeItem{Led a successful exit of the company to a strategic buyer in 2023.}
      \resumeItemListEnd
      
      \resumeSubHeadingListEnd

%
%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: Python, SQL (Postgres), NoSLQ (MongoDB), Langchain, JavaScript, HTML/CSS, Rust, GraphQL} \\
     \textbf{Frameworks}{: PyTorch, Jupyter, TypeScript, TensorFlow, React, Next.js, Node.js, TailwindCSS, FastAPI, Ollama} \\
     \textbf{Developer Tools}{: Git, Github, Docker, Google Cloud Platform, VS Code, \LaTeX} \\
     \textbf{Libraries}{: pandas, NumPy, Matplotlib, Seaborne, scikit-learn, Django, Flask, Streamlit, Beautiful Soup, Tauri, Jest} \\
    }}
 \end{itemize}
%-------------------------------------------
\end{document}